HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
abbreviating caption of fig5
on 8 pages with omri's comments out

}
\end{tabular}
\caption{Kappa versus sentence length, separately for
structural and atomic units. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure}

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME correlations with DA by HUME node type. We can see that correlation is highest where all sub-sets are taken into consideration (``all'' bar), supporting our claim for the value of taking into account a rich set of semantic phenomena. Some types of nodes seem to predict the DA scores better than others. The HUME scores on Parallel Scenes (H) and Participants (A) seem to correlate more strongly with DA than scores on Scene Main Relations (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators. We leave it to future work to construct a HUME score which weights the different node types according to their semantic relevance.\oa{I think we should be careful here. It may very well be that these stem from the number of nodes taken into account. I think we should also say explicitly that .}
This is also a demonstration of the more refined analysis (allowing to slice the data by semantic phenomena) enabled by taking a semantic approach to MT evaluation.

>>>>

}
\end{tabular}
%\caption{Kappa versus sentence length, separately for
%structural and atomic units. The numbers are the node counts in each bin. }
\caption{Kappa versus sentence length for
structural and atomic units. (Node counts in bins on top of each bar.)
}
\label{fig:iaalength}
\end{figure}

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME correlations with DA by HUME node type. We can see that correlation is highest where all sub-sets are taken into consideration (``all'' bar), supporting our claim for the value of taking into account a rich set of semantic phenomena. Some types of nodes seem to predict the DA scores better than others. The HUME scores on Parallel Scenes (H) and Participants (A) seem to correlate more strongly with DA than scores on Scene Main Relations (P+S) or linker nodes (L). Center nodes (C) are also more correlated than elaborator nodes (E), which is what we would expect given that center nodes are by definition more important to the semantics of a sentence than elaborators. We leave it to future work to construct a HUME score which weights the different node types according to their semantic relevance.
\oa{I think we should be careful here. It may very well be that these stem from the number of nodes taken into account. I think we should also say explicitly that .}
This is also a demonstration of the more refined analysis (allowing to slice the data by semantic phenomena) enabled by taking a semantic approach to MT evaluation.
